\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Asynchronously find usernames across social networks.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/poirot}{poirot \ExternalLink}} % Organization/group
    {Node.js} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}

%---------------------------------------------------------
\begin{comment}
  \cventry
    {A music streaming and recommendation service.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/Melodie}{Melodie \ExternalLink}} % Organization/group
    {Django, Scikit-learn, pandas} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}
\end{comment}
%---------------------------------------------------------
  \cventry
    {Scraped data from imdb, created a MongoDB collection, and used it to build a movie recommendation web-app using popularity based, user-user collaborative filtering, item-item collaborative filtering, and matrix factorization algorithms. Dockerized the app and deployed to heroku.} % Affiliation/role
    {\href{https://gitlab.com/rajdeepbharati/reco-engine}{mreco \ExternalLink}} % Organization/group
    {Flask, Scikit-learn, pandas} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}
    
%---------------------------------------------------------
  \cventry
    {A URL shortening service.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/PetiteURL}{PetiteURL \ExternalLink}} % Organization/group
    {Node.js, MongoDB} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}
    
%---------------------------------------------------------
  \cventry
    {A collection of python scripts to automate Facebook.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/FB-Automation}{FB Automation \ExternalLink}} % Organization/group
    {Python, Selenium} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}

%---------------------------------------------------------
  \cventry
    {Analysed twitter stream in realtime and calculated top worldwide
hashtags.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/Twitter-Realtime-Analytics}{Twitter Realtime Analytics \ExternalLink}} % Organization/group
    {Apache Storm} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}

%---------------------------------------------------------
  \cventry
    {Implemented a simple email classifier, using common Machine Learning algorithms (Naive Bayes, KNN, Decision Tree, SVM), studied their accuracy.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/Email-Classifier}{Email Classifier \ExternalLink}} % Organization/group
    {Python, Scikit-learn} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}
\begin{comment}

%---------------------------------------------------------
  \cventry
    {A collection of python scripts to automate Facebook.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/FB-Automation}{FB Automation \ExternalLink}} % Organization/group
    {Python, Selenium} % Tech
    {} % Date(s)
    {}
    \vspace{-\baselineskip}

%---------------------------------------------------------
%\begin{comment}
  \cventry
    {A collection of python scripts to automate Facebook.} % Affiliation/role
    {\href{https://github.com/rajdeepbharati/FB-Automation}{FB Automation \ExternalLink}} % Organization/group
    {Python, Selenium} % Tech
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        %\item {A collection of python scripts to automate Facebook.}
        %\item {Proposed various marketing and network activities to raise awareness.}
      \end{cvitems}
    }
    \vspace{-\baselineskip}

%---------------------------------------------------------
\end{comment}

\begin{comment}
  \cventry
    {Member} % Affiliation/role
    {PLUS (Laboratory for UNIX Security in POSTECH)} % Organization/group
    {Pohang, S.Korea} % Location
    {Sep. 2010 - Oct. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
        \item {Participated on several hacking competition and won a good award.}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{comment}
\end{cventries}
